---
title: "Summary Plots"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=5, 
                      fig.height=3,
                      dpi=300)
```

This markdown document goes over how summary plots are constructed from a table containing aggregate data.

## Load File

The code below will load the aggregate data file and create an ordered list of factors from the constructs present.It also creates a list of names associated with each channel of interest that will later be mappepd onto these factors for plot aesthetics.

```{r loaddata, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(tidyverse)

dat <- read.csv('agg_bychannel.csv', header=TRUE)
dat$construct <- factor(dat$construct,levels=  c('mp1','mp2','mtraak','mtrek1','mscl','osca12',
                                                 'tmem63a','tmem63b','trpa1','trpv4','pkd2l1','yfp'),
                        ordered = T)

names = c('mPiezo1','mPiezo2','mTraak','mTrek1','Mscl','Osca1.2','Tmem63a','Tmem63b','TrpA1','TrpV4','Pkd2L1','YFP')

dat_triage <- subset(dat, construct %in% c('mtraak','mtrek1') | seal >= 0.3)

sem <- function(x) sd(x)/sqrt(length(x))

aggthresh_dat <- data.frame(c(aggregate(thresh ~ construct,dat_triage,length),
                     aggregate(thresh ~ construct, dat_triage, max)[2],
                     aggregate(thresh ~ construct, dat_triage, mean)[2],
                     aggregate(thresh ~ construct, dat_triage, sem)[2]))
colnames(aggthresh_dat)<- c('construct','n','max', 'mean', 'sem')

aggcap_dat <- data.frame(c(aggregate(Cm ~ construct,dat_triage,length),
                     aggregate(Cm ~ construct, dat_triage, max)[2],
                     aggregate(Cm ~ construct, dat_triage, mean)[2],
                     aggregate(Cm ~ construct, dat_triage, sem)[2]))
colnames(aggcap_dat)<- c('construct','n','max', 'mean', 'sem')


```
### Subset of Table:

```{r headdat, echo=FALSE, include=TRUE}
library(knitr)
colnames(dat_triage)[1] <- "uniqueID"
kable(head(dat_triage)[1:10])
```

## Prepare plot themes and aesthetics

The following code will load the plotting libraries and font libraries to be used in creating the final plot. It also creates a custom theme function with starting plot parameters for publication quality figures.


```{r prepplot,echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(ggplot2)
library(ggbeeswarm)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(extrafont)
loadfonts(device = "win")

theme_paper <- function(base_size=10,base_family="Arial") {
  library(grid)
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text(size = 10),
            axis.text=element_text(size = 8, color = "black"),
            legend.position = "none",
            panel.border = element_blank(),
            panel.background = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid=element_blank()
      ))
}

```

## Plot Data


The following code will create the final plots of, in this case, capacitance and threshold as a function of the expressed construct. The plot is a violin plot with overlayed individual datapoints and a boxplot of the summary statistics. 
```{r pressure, echo=TRUE, include=TRUE, warning=FALSE}
library(pals)
library(cowplot)

p1 <- ggplot(dat_triage, aes(x=construct, y=thresh, fill=construct, colour=construct)) +
  geom_violin(lwd=0.25, fill='white',colour='black',scale='width')+
  geom_boxplot(color='black',width=0.1,lwd=0.2, alpha=0.4, outlier.shape =NA)+
  geom_quasirandom(shape=21, alpha=0.9, size = 1, stroke=0.25, colour='black', varwidth=T)+
  scale_x_discrete(breaks=c('mp1','mp2','mtraak','mtrek1','mscl','osca12','tmem63a','tmem63b',
                            'trpa1','trpv4','pkd2l1','yfp'), labels = names)+
  scale_colour_brewer(palette='Set3')+
  scale_fill_brewer(palette='Set3')+
  geom_text(data = aggthresh_dat, aes(x=construct, y= max + 0.1*200, 
                                   label = paste('(',n,')', sep = "")),size=2, colour='black')+
  scale_y_continuous(breaks=c(0,50,100,150,200))+
  xlab("Construct") +
  ylab("Threshold (pA)")+
  theme_paper() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)))

p1
ggsave('agg_thresh.pdf', plot=last_plot(), dpi=300, width=5, height=3, units= "in", dev=cairo_pdf)


p2 <- ggplot(dat_triage, aes(x=construct, y=Cm, fill=construct, colour=construct)) +
  geom_violin(lwd=0.25, fill='white',colour='black', scale='width')+
  geom_boxplot(color='black',width=0.1,lwd=0.2, alpha=0.4, outlier.shape =NA)+
  geom_quasirandom(shape=21, alpha=0.9, size = 1, stroke=0.25, colour='black', varwidth=T)+
  scale_x_discrete(breaks=c('mp1','mp2','mtraak','mtrek1','mscl','osca12','tmem63a','tmem63b',
                            'trpa1','trpv4','pkd2l1','yfp'), labels = names)+
  scale_colour_brewer(palette='Set3')+
  scale_fill_brewer(palette='Set3')+
  scale_y_continuous(breaks=c(0,20,40,60))+
  xlab("Construct") +
  ylab("Capacitance (pF)")+
  theme_paper() +
  theme(axis.text.x = element_text(angle=45,hjust=1),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
p2
ggsave(ggsave('agg_cap.pdf', plot=last_plot(), dpi=300, width=5, height=3, units= "in", dev=cairo_pdf))
```

