---
title: "Summary Plots"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=5, 
                      fig.height=3,
                      dpi=300)
```

This markdown document goes over how summary plots are constructed from a table containing aggregate data.

## Load File

The code below will load the aggregate data file and create an ordered list of factors from the constructs present.It also creates a list of names associated with each channel of interest that will later be mappepd onto these factors for plot aesthetics.The data is then triaged into a new dataframe called dat_triage based on having a seal quality > 300 Megaohms, a peak current greater than 150 pA.The mTraak and mTrek1 data are not subjected to this since recordings were made at 0 mV and the seal quality at the time of a given sweep cannot be reliably assessed. Finally, some aggregate functions are applied to the triaged dataset.

```{r loaddata, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(tidyverse)

dat <- read.csv('agg_bychannel.csv', header=TRUE)
dat$construct <- factor(dat$construct,levels=  c('mp1','mp2','mtraak','mtrek1','mscl','osca12',
                                                 'tmem63a','tmem63b','trpa1','trpv4','pkd2l1','yfp'),
                        ordered = T)

names = c('mPiezo1','mPiezo2','mTraak','mTrek1','Mscl','Osca1.2','Tmem63a','Tmem63b','TrpA1','TrpV4','Pkd2L1','YFP')

dat_triage <- subset(dat, construct %in% c('mtraak','mtrek1') | seal >= 0.3)
dat_triage$wthresh[dat_triage$peaki<150]=NA
sem <- function(x) sd(x)/sqrt(length(x))

dat1 <- dat %>% 
  filter((construct %in% c('mtraak', 'mtrek1')) | (seal >= 0.3)) %>%
  filter(peaki > 150) %>%
  group_by(construct) %>%
  summarize(n = length(wthresh),
            mean = mean(wthresh, na.rm=T),
            sem = sem(wthresh),
            max = max(wthresh, na.rm=T))

dat2 <- dat %>% 
  filter((construct %in% c('mtraak', 'mtrek1')) | (seal >= 0.3)) %>%
  group_by(construct) %>%
  summarize(ntot = length(wthresh))

agg_dat <- merge(dat2,dat1, all =T)

```
### Subset of triaged Data:

```{r headdat, echo=FALSE, include=TRUE}
library(knitr)
colnames(dat_triage)[1] <- "uniqueID"
kable(head(dat_triage)[1:10])
```

### Aggregate data table

```{r aggdat, echo=FALSE, include=TRUE}
kable(agg_dat)
```

## Prepare plot themes and aesthetics

The following code will load the plotting libraries and font libraries to be used in creating the final plot. It also creates a custom theme function with starting plot parameters for publication quality figures.


```{r prepplot,echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(ggplot2)
library(ggbeeswarm)
library(extrafont)
loadfonts(device = "win")

theme_paper <- function(base_size=10,base_family="Arial") {
  library(grid)
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text(size = 10),
            axis.text=element_text(size = 8, color = "black"),
            legend.position = "none",
            panel.border = element_blank(),
            panel.background = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid=element_blank()
      ))
}

```

## Plot Data

The following code will create the final plot of, in this case, Work Threshold as a function of the expressed construct. The plot is a violin plot with overlayed individual datapoints and a boxplot of the summary statistics. 
```{r pressure, echo=TRUE, include=TRUE, warning=FALSE}

p1 <- ggplot(dat_triage, aes(x=construct, y=wthresh, fill=construct, colour=construct)) +
  geom_violin(lwd=0.25, fill='white',colour='black')+
  geom_boxplot(color='black',width=0.1,lwd=0.2, alpha=0.4, outlier.shape =NA)+
  geom_quasirandom(shape=21, alpha=0.9, size = 1, stroke=0.25, colour='black', varwidth=T)+
  scale_x_discrete(breaks=c('mp1','mp2','mtraak','mtrek1','mscl','osca12','tmem63a','tmem63b',
                            'trpa1','trpv4','pkd2l1','yfp'), labels = names)+
  scale_colour_brewer(palette='Set3')+
  scale_fill_brewer(palette='Set3')+
  geom_text(data = agg_dat, aes(x=construct, y= max + 0.10*1200, 
                                   label = paste('(',n,'/',ntot,')', sep = "")),size=2, colour='black')+
  scale_y_continuous(breaks=c(250,500,750,1000,1250))+
  xlab("Construct") +
  ylab("Work Threshold (fJ)")+
  theme_paper() +
  theme(axis.text.x = element_text(angle=45,hjust=1),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
 
p1 
ggsave('agg_wthresh.pdf', plot=last_plot(), dpi=300, width=5, height=3, units= "in", dev=cairo_pdf)


```

