---
title: "Summary Plots"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=5, 
                      fig.height=3,
                      dpi=300)
```

This markdown document goes over how summary plots are constructed from a table containing aggregate data.

## Load File

The code below will load the aggregate data file and create an ordered list of factors from the constructs present.It also creates a list of names associated with each channel of interest that will later be mappepd onto these factors for plot aesthetics.

```{r loaddata, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(tidyverse)

dat <- read.csv('agg_bychannel.csv', header=TRUE)
dat$construct <- factor(dat$construct,levels=  c('mp1','mp2','mtraak','mtrek1','mscl','osca12',
                                                 'tmem63a','tmem63b','trpa1','trpv4','pkd2l1','yfp'),
                        ordered = T)

names = c('mPiezo1','mPiezo2','mTraak','mTrek1','Mscl','Osca1.2','Tmem63a','Tmem63b','TrpA1','TrpV4','Pkd2L1','YFP')

dat_triage <- subset(dat, construct %in% c('mtraak','mtrek1') | seal >= 0.3)
dat_triage$wthresh[dat_triage$peaki<150]=NA
sem <- function(x) sd(x)/sqrt(length(x))

dat1 <- dat %>% 
  filter((construct %in% c('mtraak', 'mtrek1')) | (seal >= 0.3)) %>%
  filter(peaki > 150) %>%
  group_by(construct) %>%
  summarize(n = length(wthresh),
            mean = mean(wthresh, na.rm=T),
            sem = sem(wthresh),
            max = max(wthresh, na.rm=T))

dat2 <- dat %>% 
  filter((construct %in% c('mtraak', 'mtrek1')) | (seal >= 0.3)) %>%
  group_by(construct) %>%
  summarize(ntot = length(wthresh))

agg_dat <- merge(dat2,dat1, all =T)

```
### Subset of Table:

```{r headdat, echo=FALSE, include=TRUE}
library(knitr)
colnames(dat_triage)[1] <- "uniqueID"
kable(head(dat_triage)[1:10])
```

## Prepare plot themes and aesthetics

The following code will load the plotting libraries and font libraries to be used in creating the final plot. It also creates a custom theme function with starting plot parameters for publication quality figures.


```{r prepplot,echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}

library(ggplot2)
library(ggbeeswarm)
library(extrafont)
loadfonts(device = "win")

theme_paper <- function(base_size=10,base_family="Arial") {
  library(grid)
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text(size = 10),
            axis.text=element_text(size = 8, color = "black"),
            legend.position = "none",
            panel.border = element_blank(),
            panel.background = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.grid=element_blank()
      ))
}

```

## Plot Data

The following code will create the final plot of, in this case, Threshold as a function of the expressed construct. The plot is a boxplot with overlayed individual datapoints.
```{r pressure, echo=TRUE, include=TRUE, warning=FALSE}
library(pals)
library(cowplot)
library(forcats)

p1 <- ggplot(dat_triage, aes(x=construct, y=wthresh, fill=construct, colour=construct)) +
  geom_violin(alpha=0.6, colour='gray28', lwd=0.25, outlier.shape=NA, scale="width")+
  geom_errorbar(data = agg_dat, aes(ymin = mean-sem, ymax = mean+sem, y = mean), 
                size=0.4, width=0,alpha=0.8, colour='black')+
  geom_point(data=agg_dat, aes(construct, mean+sem),shape=16,size=0.05,
             alpha=0.8,colour='black')+
  geom_point(data=agg_dat, aes(construct, mean-sem),shape=16,size=0.05,
             alpha=0.8,colour='black')+
  geom_point(data=agg_dat, aes(construct, mean), fill='white',shape=21,size=1.5, stroke=0.25,
             colour='black')+
  geom_beeswarm(shape = 21, size = 1, alpha = 0.8,cex=1, stroke=0.25, 
                   colour='black')+
  scale_x_discrete(breaks=c('mp1','mp2','mtraak','mtrek1','mscl','osca12','tmem63a','tmem63b',
                            'trpa1','trpv4','pkd2l1','yfp'), labels = names)+
  scale_colour_brewer(palette='Set3')+
  scale_fill_brewer(palette='Set3')+
  geom_text(data = agg_dat, aes(x=construct, y= max + 0.10*1200, 
                                   label = paste('(',n,'/',ntot,')', sep = "")),size=2, colour='black')+
  xlab("Construct") +
  ylab("Work Threshold (fJ)")+
  theme_paper() +
  theme(axis.text.x = element_text(angle=45,hjust=1),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
 
p1 
ggsave('agg_wthresh.pdf', plot=last_plot(), dpi=300, width=5, height=3, units= "in", dev=cairo_pdf)


```

